---
title: What are XmR Charts?
subtitle: And how can they help you monitor performance
author: Robert Muwanga
date: '2023-05-18'
slug: what-are-xmr-charts
categories:
  - blog
  - R
tags:
  - performance management
description: ''
externalLink: ''
series: []
draft: True
---

```{r import_libraries}
library(tidyverse)
library(gt)
```
As a manager, one of your biggest challenges is being able to identify opportunities - I prefer calling it opportunities instead of "problems" - where we can improve the performance of a process under our control. 

Let's put this into context. As a manager you may be responsible for the performance of a consistent, sequential process that involves receiving stock from suppliers: 

+ The delivery truck docks at the delivery point in the warehouse.
+ You confirm the stock in truck using the invoice that was sent to your email.
+ You sign the delivery note.
+ Your staff off-load the truck contents and systematically index, update the warehousing system, and store the physical items on the respective shelves.
+ You physically re-confirm the stock vis-à-vis what was put in the system and sign off the process.

I’m not an expert in this space but let’s go with this.

You see the speed of execution as one of the metrics that he uses to track performance. Related to this metric, you are interested in understanding whether the process is working well consistently or improving, or whether you needs to quickly discover whether a review of the process needs to be done if its taking longer than expected.

As a dedicated manager, you has been tracking the daily performance of the process and have a basic tracker that looks something like this:

```{r data}
data <- 
```