---
title: Exploring the Gap Minder Dataset
author: Robert Muwanga
date: '2023-01-14'
slug: exploring-the-gap-minder-dataset
categories:
  - blog
  - R
tags: []
description: ''
externalLink: ''
series: []
draft: true
---

```{r setup}

packages <- c("tidyverse", "gapminder", "plotly", "gt") # Include packages of interest
packages_not_installed <- !(packages %in% installed.packages())

if(sum(packages_not_installed) > 0) { # Install missing packages
  install.packages(
    packages[packages_not_installed])
}

purrr::walk(.x = packages, ~require(package = .x, character.only = TRUE)) # Load missing packages
data("gapminder", package = 'gapminder') # Load the gapminder dataset

```

## Introduction

*Gapminder.org* is a non-profit organisation whose mission is to rid the world of global misconceptions. It does this in 3 ways:

1. Asking thousand of fact-based questions to the public in many countries to see what their view of the world is like.
2. Cross-checking this feedback with verifiable and reliable data sources such as the UN to identify the most common misconceptions where people's ideas differ from reality.
3. Communicate the facts, and help one upgrade their worldview.

Visit their website for more information and how you can participate.

## Purpose of this exercise

I shall be using the gapminder dataset to build a couple of visualisations as a means of not only practicing my skillsets but also to answer some interesting questions.

## Overview of the data

The gapminder dataset consists of `r nrow(gapminder)` observations and `r ncol(gapminder)` variables. 

```{r}
gapminder |> 
  gt() |>
  fmt_number(columns = lifeExp:gdpPercap, drop_trailing_zeros = TRUE) |>
  cols_label(
    country = "Country", 
    continent = "Continent", 
    year = "Year", 
    lifeExp = "Average Life Expectancy (Years)", 
    pop = "Population", 
    gdpPercap = "GDP Per Capita (US$)"
  )
```